\mythesistitleNOTSYNPOSIS

### 2012-02-24 src/010chap1.tex
spell check completed final version
shit just got really real.

% \tnote{testing 1 2 3...}%
% \tnote[bogus1]{testing 1 2 3...}%
% \tnote[important]{testing 1 2 3...}% 
% \tnote[dire]{testing 1 2 3...}% 
% \tnote[minor]{testing 1 2 3...}% 
% \tnote[pressing]{testing 1 2 3...}% 
% \tnote[UNDEF]{testing 1 2 3...}%

@@

The idea of \cop of binary matrices was mentioned a few times in
earlier sections. Now we will see the formal definition of \COP in
Definition~\ref{{def:copmatrix}}.

@@

The equivalence of the problem of testing for the consecutive-ones
property to the constraint statisfaction problem of interval
assignment \cite{nsnrs09} or interval labeling \cite{kklv10} is as
follows. Every column (row) of the binary matrix can be converted into
a set of non-negative integers which are the indices of rows (columns)
with {\un}s in that column (row). It is apparent that if the matrix
has COP in columns (rows), then constructing such sets after applying
the COP permutation to the rows (columns) of the matrix will result in
sets with consecutive integers. In other words, after application of
COP reordering, the sets are intervals. Indeed the problem now becomes
finding interval assignments to a given set system such that there
exists a permutation of the universe of set of row indices (column
indices) which converts each set to its assigned interval.

>>>>

@@

The idea of \cop of binary matrices was mentioned a few times in
earlier sections. Now we will see the formal definition of \COP in
Definition~\ref{def:copmatrix}.

@@

The equivalence of the problem of testing for the consecutive-ones
property to the constraint satisfaction problem of interval
assignment \cite{nsnrs09} or interval labeling \cite{kklv10} is as
follows. Every column (row) of the binary matrix can be converted into
a set of non-negative integers which are the indices of rows (columns)
with {\un}s in that column (row). It is apparent that if the matrix
has COP in columns (rows), then constructing such sets after applying
the COP permutation to the rows (columns) of the matrix will result in
sets with consecutive integers. In other words, after application of
COP reordering, the sets are intervals. Indeed the problem now becomes
finding interval assignments to a given set system such that there
exists a permutation of the universe of set of row indices (column
indices) which converts each set to its assigned interval.

### 2012-02-24 src/020chap2.tex
spell check completed final version
shit just got really real.

In this section and the rest of the chapter we see results that shaped the
correponding areas respectively for \cop in binary matrices.

@@

\cite{at72} discovered certain forbidden structures for convex
bipartite graphs\footnote{The terminology in \cite{at72} differs. It
  uses the term {\em graphs with $V_1$-consecutive arragement} instead
  of {\em convex bipartite graphs}.} and by definition of this graph
class, this translates to a set of forbidden submatrices for matrices
with \cop.  The following are the theorems from \cite{at72} that
acheived this characterization.

Theorem~\ref{th:tuckeratfree} states that convex bipartite graphs
cannot have {\em asteroidal triples} (see
Definition~\ref{def:asteroidal}) contained in the corresponding vertex
partition. This partition of the bipartite graph corresponds to
columns (rows) if its half adjacency matrix has \COP columns (rows).
Theorem~\ref{th:tuckerforbidden} lists the structures in a bipartite
graph that force one of its vertex partitions to have asteriodal
triples -- in other words, it identifies the subgraphs that prevent
the graph from being convex bipartite.

\begin{definition}[Asteroidal triple]
  \label{def:asteroidal}
  % If $G = (V,E)$ is a graph, a set of three vertices from $V$ form
  % an {\em asteroidal triple} if between any two of them there exists
  % a path in $G$ that does not contain any vertex from the closed
  % neighborhood of the third vertex.
  An {\em asteroidal triple} in a graph $G$ is a tuple of vertices
  $\{v_1,v_2,v_3\} \subset V$ such that between every pair of vertices
  from this tuple there exists a path that avoids the closed
  neighbourbood of the third vertex.
\end{definition}

@@

\begin{definition}[{\em \Cop for set systems}]%
  \label{def:matrixsetsystem}%
  % [\emph{Set system of a binary matrix}.]
  Let $M$ be a binary matrix of order $n \times m$ and $\{c_i \mid i
  \in [m]\}$ be the columns in $M$.  A set system $\cF_{M} = \{S_i
  \mid S_i \subseteq [n], i \in [m]\}$ is defined such that for every
  column $c_i$ of $M$, set $S_i = \{j \mid m_{ji} = \un \}$. The
  collection $\cF_M$ is the {\em set system of binary matrix} $M$. The
  {\em binary matrix for set system} $\cF$ is conversely constructed
  and denoted by $M^\cF$. Thus, $M^{\cF_M} = M$.%
  \par\noindent%
  A set system $\cF$ from universe $U$, $|U| = n$ has the {\em \cop}
  if there exists a linear order or permutation $\sigma = w_1w_2\ldots
  w_n$ that can be applied to $U$ \stt each set $S \in \cF$ becomes a
  consecutive subsequence (also termed an {\em interval})
  $w_{i}w_{i+1}\ldots w_{i+k-1}$ on $\sigma$ for some positive integer
  $i \le n+1-k$ where $k = |S|$.
  \par\noindent%
  The set $\valid{U,\cF}$ respresents all \COP orders of $\cF$ in $U$.
  \dstop
\end{definition}

@@

  \item $\cF$ is called {\em complete}\footnote{\cite{mcc04} calls
      this a {\em weakly partative family}. \label{mcc2}} if the
    following hold true for every pair of non-orthogonal (overlapping)
    sets $A, B$ in $\cF$.

@@

  \item \label{def::slashop} The binary operator $/$ is defined as
    follows. Let $A, B$ be two sets from set sysetm $\cF$.
    \begin{align*}
      A/B &= A \setminus B \cup \{b\}\\
      \cF/B &= \{ S/B \mid S \in \cF, S \nsubseteq B \}
    \end{align*}
    $b$ is a new element added as a representative for $B$.
 \end{enumerate}
  \dstop
\end{definition}

@@

\begin{theoremsansproof}[{\cite[Th.~9]{mm96}}] %,\cite[Th.~2.1]{mcc04}
\label{th:pqrfinalmm}
If $\cF$ is a set system with universe $U$ and $|U| \ge 3$ then one of
the following statements hold.
\begin{enumerate}
\item \label{th::it1} $\overline{\cF} = \cT(U)$ 
\item \label{th::it2}$\overline{\cF} = consec(\alpha)$ for
  some permutation $\alpha$ on $U$ ($consect(\alpha)$ is a linear order)
\item \label{th::it3}$\overline{\cF} = \power{U}$ 
\end{enumerate}
\end{theoremsansproof}

@@

\subsubsection{Comparision with generalized \PQtree}

Stepping back a little, the reader may have noticed the cross
references between \PQRtree and other data structures in footnotes
earlier.  Generalized \PQtree or \gPQtree is a data structure defined
in \cite{n89} to represent all orthogonal sets of a set system
$\cF$. A data structure with the same name was later defined in
\cite{mcc04} as part of a {\em substitution decomposition} for a set
system $\cF$ and subsequently \cite{mcc04} gives a new
characterization of $\cF$ using a so-called incompatibility graph
(this is discussed in more detail in
Section~\ref{sec:incompatibilitygr}). As seen above, \PQRtree is
defined in \cite{mm96} as a data structure to represent any set system
$\cF$ with additional information in their $R$-nodes if $\cF$ has no
\COP. All three of these data structures are proposed as
generalizations of \cite{bl76}'s \PQtree and hence produce the \PQtree
if $\cF$ has \COP. As a whole, all these three data strutures are
largely identical with their differences being notional. We discussed
the basic theory that they all hold and predominantly used the
terminology from \cite{mm96}. To the best of our knowledge this
comparison study has not been made earlier in the literature.  We
observe the three data strutures of \PQRtree, \gPQtree and generalized
\PQtree to be equivalent. The terminologies of the theory of all these
data structures is summarised in Table~\ref{tab:pqrcomparison}.

@@

      &
    Complete collection &
    Weakly partative family
    \\\hline

@@

The necessity condition of Theorem~\ref{th:icpia1} is fairly
obvious. It turns out that it is sufficient too.  This is demostrated
by two algorithms which work as follows. The first one iterates over
the assignment $\Pi$ %set system $\cF$
and changes it in each iteration till the altered
assignment %set system
has no more overlapping intervals (intervals are the second
  element in each ordered pair of $\Pi$. Def.~\ref{def:icpia}) %sets
\cite[Alg.~1]{nsnrs09}. This is acheived by replacing two overlapping
assignment pairs $(A_i, B_i)$ and $(A_j, B_j)$ with the partitions of
$(A_i \cup A_j,B_i \cup B_j)$ induced by their overlaps -- $(A_i
\setminus A_j, B_i \setminus B_j)$, $(A_i \cap A_j, B_i \cap B_j)$ and
$(A_j \setminus A_i, B_j \setminus B_i)$.

@@

The procedure used to prove Theorem~\ref{th:forbiddenalg} is as
follows. 
\begin{enumerate}
\item Run the algorithm mentioned in
  Propostition~\ref{prop:tuckerdomapprox} to obtain a submatrix $A$
  which is an approximation of the smallest forbidden submatrix. (If
  the actual solution is $M_{I_k}$ or $M_{II_k}$ this will be an exact
  solution.)
\item Run the algorithm from Propostition~\ref{cor:miiitime} to find
  an induced $M_{III_k}$ and let this be $B$.
\item Run the algorithm from Corollary~\ref{cor:mivmvpolytime} twice
  -- once each for finding $M_{IV}$ and finding $M_{V}$. Let the
  results be $C$ and $D$ respectively.
\item Return the minimum size matrix among $A, B, C, D$ (minimum size
  being one of the following: number of rows, number of columns, sum
  of number of rows and columns, number of {\un} entries).
\end{enumerate}

@@

When a \COP test algorithm reports negative, it is hard to verify
this. While \cite{at72} gives forbidden substructures for \COP, there
are no efficient algorithms to find these strutures in a matrix. In
fact, \cite{v82} shows that even finding a forbidden submatrix with at
least $k$ rows in an input matrix is NP-complete. This was proven by
polynomially reducing the longest path problem for graphs to this
problem.

\cite{mcc04} describes another characterization for matrices without
\COP which is efficiently computable. This is done by way of an {\em
  incompatibility graph} of a set system (since \COP in
  matrices and set systems are equivalent problems as seen in
  Section~\ref{sec:surveycertalgo} we will use the term set system in
  this section, in line with \cite{mcc04}'s convention). The
construction of this graph is based on the following observation.

\begin{observation} 
  Consider elements $a, b, c \in U$ and a set system $\cF$ with
  universe $U$. If there is at least one set $S \in \cF$ \stt $a, c
  \in S$ but $b \notin S$, then it is impossible to have a \COP order
  that will place $b$ in between $a$ and $c$. \tnote[important]{also cite the
    inbetweenness problem}
\end{observation}

For the sake of argument, suppose there exists such a \COP
order. Clearly, it will not succeed in mapping $S$ to an interval
since $b \notin S$ which is a contradiction to the assumption that
this is a \COP order.  The ordered pair $(x,y)$ denotes that in the
\COP order $y$ comes after $x$. Based on above observations, this
means $(a,b)$ and $(b,c)$ are not compatible in any \COP order. So are
$(c,b)$ and $(b,a)$.  Thus a binary relation {\em is incompatible
  with} on $U \times U \setminus \{(a,a) \mid a \in U\}$ can be
defined based on the membership of elements of $U$ in the sets in
$\cF$.  \cite{mcc04} creates an incompatiblity graph with vertices
denoting ordered pairs and edges denoting the incompatibility
relation.

>>>>

In this section and the rest of the chapter we see results that shaped the
corresponding areas respectively for \cop in binary matrices.

@@

\cite{at72} discovered certain forbidden structures for convex
bipartite graphs\footnote{The terminology in \cite{at72} differs. It
  uses the term {\em graphs with $V_1$-consecutive arrangement} instead
  of {\em convex bipartite graphs}.} and by definition of this graph
class, this translates to a set of forbidden submatrices for matrices
with \cop.  The following are the theorems from \cite{at72} that
achieved this characterization.

Theorem~\ref{th:tuckeratfree} states that convex bipartite graphs
cannot have {\em asteroidal triples} (see
Definition~\ref{def:asteroidal}) contained in the corresponding vertex
partition. This partition of the bipartite graph corresponds to
columns (rows) if its half adjacency matrix has \COP columns (rows).
Theorem~\ref{th:tuckerforbidden} lists the structures in a bipartite
graph that force one of its vertex partitions to have asteroidal
triples -- in other words, it identifies the subgraphs that prevent
the graph from being convex bipartite.

\begin{definition}[Asteroidal triple]
  \label{def:asteroidal}
  % If $G = (V,E)$ is a graph, a set of three vertices from $V$ form
  % an {\em asteroidal triple} if between any two of them there exists
  % a path in $G$ that does not contain any vertex from the closed
  % neighborhood of the third vertex.
  An {\em asteroidal triple} in a graph $G$ is a tuple of vertices
  $\{v_1,v_2,v_3\} \subset V$ such that between every pair of vertices
  from this tuple there exists a path that avoids the closed
  neighbourhood of the third vertex.
\end{definition}

@@

\begin{definition}[{\em \Cop for set systems}]%
  \label{def:matrixsetsystem}%
  % [\emph{Set system of a binary matrix}.]
  Let $M$ be a binary matrix of order $n \times m$ and $\{c_i \mid i
  \in [m]\}$ be the columns in $M$.  A set system $\cF_{M} = \{S_i
  \mid S_i \subseteq [n], i \in [m]\}$ is defined such that for every
  column $c_i$ of $M$, set $S_i = \{j \mid m_{ji} = \un \}$. The
  collection $\cF_M$ is the {\em set system of binary matrix} $M$. The
  {\em binary matrix for set system} $\cF$ is conversely constructed
  and denoted by $M^\cF$. Thus, $M^{\cF_M} = M$.%
  \par\noindent%
  A set system $\cF$ from universe $U$, $|U| = n$ has the {\em \cop}
  if there exists a linear order or permutation $\sigma = w_1w_2\ldots
  w_n$ that can be applied to $U$ \stt each set $S \in \cF$ becomes a
  consecutive subsequence (also termed an {\em interval})
  $w_{i}w_{i+1}\ldots w_{i+k-1}$ on $\sigma$ for some positive integer
  $i \le n+1-k$ where $k = |S|$.
  \par\noindent%
  The set $\valid{U,\cF}$ represents all \COP orders of $\cF$ in $U$.
  \dstop
\end{definition}

@@

  \item $\cF$ is called {\em complete}\footnote{\cite{mcc04} calls
      this a {\em weakly partitive family}. \label{mcc2}} if the
    following hold true for every pair of non-orthogonal (overlapping)
    sets $A, B$ in $\cF$.

@@

  \item \label{def::slashop} The binary operator $/$ is defined as
    follows. Let $A, B$ be two sets from set system $\cF$.
    \begin{align*}
      A/B &= A \setminus B \cup \{b\}\\
      \cF/B &= \{ S/B \mid S \in \cF, S \nsubseteq B \}
    \end{align*}
    $b$ is a new element added as a representative for $B$.
 \end{enumerate}
  \dstop
\end{definition}

@@

\begin{theoremsansproof}[{\cite[Th.~9]{mm96}}] %,\cite[Th.~2.1]{mcc04}
\label{th:pqrfinalmm}
If $\cF$ is a set system with universe $U$ and $|U| \ge 3$ then one of
the following statements hold.
\begin{enumerate}
\item \label{th::it1} $\overline{\cF} = \cT(U)$ 
\item \label{th::it2}$\overline{\cF} = consec(\alpha)$ for
  some permutation $\alpha$ on $U$ ($consec(\alpha)$ is a linear order)
\item \label{th::it3}$\overline{\cF} = \power{U}$ 
\end{enumerate}
\end{theoremsansproof}

@@

\subsubsection{Comparison with generalized \PQtree}

Stepping back a little, the reader may have noticed the cross
references between \PQRtree and other data structures in footnotes
earlier.  Generalized \PQtree or \gPQtree is a data structure defined
in \cite{n89} to represent all orthogonal sets of a set system
$\cF$. A data structure with the same name was later defined in
\cite{mcc04} as part of a {\em substitution decomposition} for a set
system $\cF$ and subsequently \cite{mcc04} gives a new
characterization of $\cF$ using a so-called incompatibility graph
(this is discussed in more detail in
Section~\ref{sec:incompatibilitygr}). As seen above, \PQRtree is
defined in \cite{mm96} as a data structure to represent any set system
$\cF$ with additional information in their $R$-nodes if $\cF$ has no
\COP. All three of these data structures are proposed as
generalizations of \cite{bl76}'s \PQtree and hence produce the \PQtree
if $\cF$ has \COP. As a whole, all these three data structures are
largely identical with their differences being notional. We discussed
the basic theory that they all hold and predominantly used the
terminology from \cite{mm96}. To the best of our knowledge this
comparison study has not been made earlier in the literature.  We
observe the three data structures of \PQRtree, \gPQtree and generalized
\PQtree to be equivalent. The terminologies of the theory of all these
data structures is summarised in Table~\ref{tab:pqrcomparison}.

@@

      &
    Complete collection &
    Weakly partitive family
    \\\hline

@@

The necessity condition of Theorem~\ref{th:icpia1} is fairly
obvious. It turns out that it is sufficient too.  This is demonstrated
by two algorithms which work as follows. The first one iterates over
the assignment $\Pi$ %set system $\cF$
and changes it in each iteration till the altered
assignment %set system
has no more overlapping intervals (intervals are the second
  element in each ordered pair of $\Pi$. Def.~\ref{def:icpia}) %sets
\cite[Alg.~1]{nsnrs09}. This is achieved by replacing two overlapping
assignment pairs $(A_i, B_i)$ and $(A_j, B_j)$ with the partitions of
$(A_i \cup A_j,B_i \cup B_j)$ induced by their overlaps -- $(A_i
\setminus A_j, B_i \setminus B_j)$, $(A_i \cap A_j, B_i \cap B_j)$ and
$(A_j \setminus A_i, B_j \setminus B_i)$.

@@

The procedure used to prove Theorem~\ref{th:forbiddenalg} is as
follows. 
\begin{enumerate}
\item Run the algorithm mentioned in
  Proposition~\ref{prop:tuckerdomapprox} to obtain a submatrix $A$
  which is an approximation of the smallest forbidden submatrix. (If
  the actual solution is $M_{I_k}$ or $M_{II_k}$ this will be an exact
  solution.)
\item Run the algorithm from Proposition~\ref{cor:miiitime} to find
  an induced $M_{III_k}$ and let this be $B$.
\item Run the algorithm from Corollary~\ref{cor:mivmvpolytime} twice
  -- once each for finding $M_{IV}$ and finding $M_{V}$. Let the
  results be $C$ and $D$ respectively.
\item Return the minimum size matrix among $A, B, C, D$ (minimum size
  being one of the following: number of rows, number of columns, sum
  of number of rows and columns, number of {\un} entries).
\end{enumerate}

@@

When a \COP test algorithm reports negative, it is hard to verify
this. While \cite{at72} gives forbidden substructures for \COP, there
are no efficient algorithms to find these structures in a matrix. In
fact, \cite{v82} shows that even finding a forbidden submatrix with at
least $k$ rows in an input matrix is NP-complete. This was proven by
polynomially reducing the longest path problem for graphs to this
problem.

\cite{mcc04} describes another characterization for matrices without
\COP which is efficiently computable. This is done by way of an {\em
  incompatibility graph} of a set system (since \COP in matrices and
set systems are equivalent problems as seen in
Section~\ref{sec:surveycertalgo} we will use the term set system in
this section, in line with \cite{mcc04}'s convention). The
construction of this graph is based on the following observation. A
similar observation was made in \cite{co98} in relation to the
betweenness problem in computational biology.

\begin{observation} 
  Consider elements $a, b, c \in U$ and a set system $\cF$ with
  universe $U$. If there is at least one set $S \in \cF$ \stt $a, c
  \in S$ but $b \notin S$, then it is impossible to have a \COP order
  that will place $b$ in between $a$ and $c$. 
\end{observation}

For the sake of argument, suppose there exists such a \COP
order. Clearly, it will not succeed in mapping $S$ to an interval
since $b \notin S$ which is a contradiction to the assumption that
this is a \COP order.  The ordered pair $(x,y)$ denotes that in the
\COP order $y$ comes after $x$. Based on above observations, this
means $(a,b)$ and $(b,c)$ are not compatible in any \COP order. So are
$(c,b)$ and $(b,a)$.  Thus a binary relation {\em is incompatible
  with} on $U \times U \setminus \{(a,a) \mid a \in U\}$ can be
defined based on the membership of elements of $U$ in the sets in
$\cF$.  \cite{mcc04} creates an incompatibility graph with vertices
denoting ordered pairs and edges denoting the incompatibility
relation.

### 2012-02-24 src/030chap3.tex
spell check completed final version
shit just got really real.

\begin{lemma}[{\cite[Lem.~1]{nsnrs09}}]
  \label{lem:intersection-cardinality} 
  Let $P$ be a path, $S_1, S_2, S_3$ be 3 sets, and $T_1, T_2, T_3$ be
  paths from $P$, such that $|S_i \cap S_j |=|T_i \cap T_j|, 1 \leq
  i,j \leq 3$.  Then, $|S_1 \cap S_2 \cap S_3| = |T_1 \cap T_2 \cap
  T_3|$.
\end{lemma}
\begin{lemma}[{\cite[Th.~2]{nsnrs09}}]
  \label{lem:icpia} 
  A path labeling $(\cF, \cl)$ with target tree $T$ as a path is
  feasible iff it is an ICPIA.
\end{lemma}

@@

Since their pre-images have been found, all leaves in $T$ are then
pruned away. The leaf labels are removed from the path labeling
$\cl_2$ and the corresponding elements are removed from the
corresponding sets in $\cF_2$. It is now clear that we have a
subproblem with a new hypergraph $\cF'$, new tree path labeling $\cl'$
and target tree $T'$.  The tree pruning algorithm is recursively
called on $\cF', \cl', T'$. The recursive call returns the bijection
$\phi''$ for the rest of the elements in $supp(\cF)$ which along with
the leaf labels $\phi'$ computed earlier gives us a hypergraph
isomorphism $\phi$ for the input $\cF,\cl,T$.  
Lemma~\ref{lem:hyperiso} proves the correctness of this computation.

>>>>

\begin{lemma}[{\cite[Lem.~1]{nsnrs09}}]
  \label{lem:intersection-cardinality} 
  Let $P$ be a path, $S_1, S_2, S_3$ be 3 sets, and $T_1, T_2, T_3$ be
  paths from $P$, such that $|S_i \cap S_j |=|T_i \cap T_j|, 1 \leq
  i,j \leq 3$.  Then, $|S_1 \cap S_2 \cap S_3| = |T_1 \cap T_2 \cap
  T_3|$.
\end{lemma}
\begin{lemma}[{\cite[Th.~2]{nsnrs09}}]
  \label{lem:icpia} 
  A path labeling $(\cF, \cl)$ with target tree $T$ as a path is
  feasible \iff it is an ICPIA.
\end{lemma}

@@

Since their preimages have been found, all leaves in $T$ are then
pruned away. The leaf labels are removed from the path labeling
$\cl_2$ and the corresponding elements are removed from the
corresponding sets in $\cF_2$. It is now clear that we have a
subproblem with a new hypergraph $\cF'$, new tree path labeling $\cl'$
and target tree $T'$.  The tree pruning algorithm is recursively
called on $\cF', \cl', T'$. The recursive call returns the bijection
$\phi''$ for the rest of the elements in $supp(\cF)$ which along with
the leaf labels $\phi'$ computed earlier gives us a hypergraph
isomorphism $\phi$ for the input $\cF,\cl,T$.  
Lemma~\ref{lem:hyperiso} proves the correctness of this computation.

### 2012-02-24 src/040chap4.tex
- incorporated new changes to Characterization algorithm. no more exit    statements in algo 1 and 2. however it is not identitcal to n's    version. kept some of the old lemmas because it seems to elucidate    (to me) the thesis. - partial editing done of general tree section (prime matrix theory)    -- TBD - not sure about status of special tree = path section -- TBD
- changed notation for induced path labeling
- changed filter 1 and 2 names.
- poset definition
spell check completed final version
shit just got really real.

\def\p{{\sc P}\xspace}
\def\gicomplete{{\sc GI}-complete\xspace}
\def\logspace{{\sc logspace\xspace}\xspace}
\def\ptime{{\sc ptime}\xspace}
\def\fpplusc{{\sc FP+C}\xspace}

@@

In this thesis, we surveyed \cop testing algorithms and as new results
we gave a characterization for a generalization of \COP, namely,
feasible tree path labeling of path hypergraphs. The proof for this is
constructive and computes a feasibility bijection mapping vertices of
the hypergraph to vertices of the given target tree. We also described
an exponential algorithm that computes a feasible TPL to a given
hypergraph if it is a path hypergraph.  In this chapter we will see a
few ideas where tree path labeling, in our experience, shows promising
scope for futher research.

@@

\textbf{Graph isomorphism and logspace canonization.}  Canonization is
an important tool in graph isomorphism. Invention of a deterministic
method of canonization for any class of graphs naturally results in an
algorithm for isomorphism. All that is required is to check if the
canons of two graphs are the same. Thus one way to study the
complexity of graph isomorphism is by studying canonization
methods. While general graph ismorphism remains elusive in terms of
hardness, canonization has been studied for smaller classes of graphs
thus giving complexity or hardness results for them -- some of the
canonization results are \cite{sl92,dlntw09,adkk09,kklv10}.

@@

%\noindent
\textbf{Complexity of TPL in other tree classes.}  We know that on
intervals, \CFTPL is easy (Section~\ref{sec:icpplicpia}).  We showed
that \CFTPL on {\kstar} is also polynomial time solvable in
Section~\ref{sec:ksubdivstar}. However, due to its close connections
with path graph isomorphism which is \gicomplete \cite{kklv10}, we
conjecture that \CFTPL on general trees cannot do better than
\gicomplete. Our algorithm in Section~\ref{sec:decompos} is unable to
solve it in \p. It would therefore, be certainly of interest to
classify the kinds of trees and hypergraphs for which feasible path
labelings can be found efficiently, or better still, to solve \CFTPL
for general trees itself in \p-time or prove that it is not in \p.

>>>>

@@

In this thesis, we surveyed \cop testing algorithms and as new results
we gave a characterization for a generalization of \COP, namely,
feasible tree path labeling of path hypergraphs. The proof for this is
constructive and computes a feasibility bijection mapping vertices of
the hypergraph to vertices of the given target tree. We also described
an exponential algorithm that computes a feasible TPL to a given
hypergraph if it is a path hypergraph.  In this chapter we will see a
few ideas where tree path labeling, in our experience, shows promising
scope for further research.

@@

\textbf{Graph isomorphism and logspace canonization.}  Canonization is
an important tool in graph isomorphism. Invention of a deterministic
method of canonization for any class of graphs naturally results in an
algorithm for isomorphism. All that is required is to check if the
canons of two graphs are the same. Thus one way to study the
complexity of graph isomorphism is by studying canonization
methods. While general graph isomorphism remains elusive in terms of
hardness, canonization has been studied for smaller classes of graphs
thus giving complexity or hardness results for them -- some of the
canonization results are \cite{sl92,dlntw09,adkk09,kklv10}.

@@

%\noindent
\textbf{Complexity of TPL in other tree classes.}  We know that on
intervals, \CFTPL is easy (Section~\ref{sec:icpplicpia}).  We showed
that \CFTPL on {\kstar} is also polynomial time solvable in
Section~\ref{sec:ksubdivstar}. However, due to its close connections
with path graph isomorphism which is \gicomplete \cite{kklv10}, we
conjecture that \CFTPL on general trees cannot do better than
\gicomplete. Our algorithm in Section~\ref{sec:norestraint} is unable to
solve it in \p. It would therefore, be certainly of interest to
classify the kinds of trees and hypergraphs for which feasible path
labelings can be found efficiently, or better still, to solve \CFTPL
for general trees itself in \p-time or prove that it is not in \p.
